---
title: "RENEW Data Report"
author: "Magali Blanco"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
editor_options: 
  chunk_output_type: console
---


**To do:**   
### --> double check Q numbers     
### --> add "prefer not to answer to all Qs?
 
# Summary of script  

This report summarizes the data collected for the RENEW Study from homecare aide peer navigators and homecare aides who called the peer navigator line. Specifically, it summarizes:

* Peer navigators   
  - Initial questionnaire   
  - Training evaluation   
  - Training quizzes    

* Homecare aides   
  - Pre-program questionnaire 

 
\newpage

### --> check that correct HCA blank surveys are dropped (at the end) 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache=T, cache.comments = F, message = F, warning = F, tidy.opts=list(width.cutoff=60), tidy=TRUE, fig.height = 8)  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
      detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

pacman::p_load(readxl, tidyverse, knitr, kableExtra,
               qwraps2
               )

source("Var&Fns.R")

```

```{r}
# set common variables

#n_digits <- 0
show_denom <- "never"

# for correct formating
options(qwraps2_markup = "markdown", 
        qwraps2_frmt_digits = 0)

```

```{r}
######################################### Load data #########################################

pn_dem <- read_excel(file.path("Data", "Peer Navigators", "peer navigator initial questionnaires.xlsx"))
pn_train_eval <- read_excel(file.path("Data", "Peer Navigators", "peer navigator training evaluations.xlsx"))
pn_quiz <- read_excel(file.path("Data", "Peer Navigators", "peer navigator training quizzes.xlsx"))

hca0 <- read_excel(file.path("Data", "HCA", "Pre-Program Questionnaire, 4-20.xlsx")) %>%
  slice(-c(1:2)) %>%
  ### --> fix Q2.6 (if using) to date if it's a string
  mutate(
    
      )



#Peer navigators
pn_quiz <- pn_quiz %>%
  mutate(
    #recode supervisor
    id = recode(id, Supervisor = "999")) %>%
  #convert character columns to numbers 
  mutate_if(is.character, as.numeric) %>%
  # drop individuals who only completed 1 survey
  filter(!id %in% c(2, 3))


# HCA
hca <- hca0 %>%
  # drop blank surveys. Using this question as an example. 
  
  # ---> DOUBLE CHECK at end. 
  
  drop_na(Q2.49_1) %>%
   mutate(
    Q2.2_num = Q2.2,
    Q2.2 = recode_factor(factor(Q2.2),
                         "1" = "Injury at work",
                         "2" = "Injury not at work",
                         "3" = "Pain while working",
                         "4" = "Pain outside of work",
                         "5" = "Preventing injury/safety concern",
                         "6" = "Prefer not to answer"
                         )
    ) %>%
  #make these responses numeric
  mutate_at(vars(Q2.52_1_TEXT, Q2.43_1_TEXT, Q2.45_1_TEXT, Q2.46,
                 contains(c("Q2.49", "Q2.50"))
                 ), ~as.numeric(.)) 

```


# Peer Navigators 

```{r}
######################################### Peer Navigators #########################################
###################################################################################################


### --> ?? no "English as primary langugae" Q. get from benefits group?

```

## Demographics 

From initial Questionnaires 

```{r}

```


```{r}
######################################### Demographics #########################################
#Table 1 for peer navigators
pn_dem %>%
  t1.fn(column.name = "Peer Navigators") %>%
  filter(substr(x = get("Peer Navigators"), 1,1) != "0") %>%
  kable(caption = "Participant Demographics & Work Characteristics", 
        #format = "latex"
        ) %>%
  pack_rows("Race", 4, 7,  bold = F, label_row_css = F) %>%
  pack_rows("Education", 9, 11, label_row_css = F,  bold = F) %>%
  #work around since bold=F doesn't work in pack_rows()  
  gsub(pattern = "(<strong>)|<strong/>", replacement = "")
 
```

## Chronic Pain (n, %)

```{r}
######################################### Chronic Pain #########################################

pn_pain_known = sum(!is.na(pn_dem$chronic_pain))
pn_pain_yes_n = sum(pn_dem$chronic_pain == 1, na.rm = T)
pn_pain_yes_pct = paste0(mean(pn_dem$chronic_pain, na.rm = T)*100)

pn_pain_n_pct <- paste0(pn_pain_yes_n, " (", pn_pain_yes_pct, "%)") 

pn_pain_n_pct %>%
  kable(col.names = "Peer Navigators", 
        caption = "History of chronic musculoskeletal pain")

```

## Training evaluations

Excludes:   

* open ended responses    

```{r}
######################################### Training Evaluations #########################################
# w/o supervisor
pn_train_eval %>%
  #drop supervisor & 2 PNs that didn't complete survey 
  filter(id != "supervisor") %>%
  training.eval.fn() %>%
  kable(caption = "Peer Navigators Training and Program Feedback. Number (%) of individuals who 'Agree' or 'Strongly Agree'. Excludes supervisor.",  
        col.names = c("Measure", "1", "2"),  
        ) %>%
  add_header_above(c(" " = 1, "Training" = 2))  
 #cat(., file = "df.html") 

```

```{r}
# w/ supervisor
pn_train_eval %>%
  #drop supervisor & 2 PNs that didn't complete survey 
  training.eval.fn() %>%
  kable(caption = "Peer Navigators Training and Program Feedback. Number (%) of individuals who 'Agree' or 'Strongly Agree'. Includes supervisor.",  
        col.names = c("Measure", "1", "2"),  
        ) %>%
  add_header_above(c(" " = 1, "Training" = 2))  
  
```

## Quizzes

```{r}
######################################### Quizzes #########################################

max_score <- 16

pn_quiz <- pn_quiz %>%
  #drop supervisor
  filter(id != 999) %>%
  #label correct answers based on whether individuals received full credit
  mutate(
    wc_benefits_cor = as.numeric(wc_benefits == 5),
    wc_medical_coverage_cor = as.numeric(wc_medical_coverage == 1),
    on_job_injuries_cor = as.numeric(on_job_injuries == 4),
    smoking_cor = as.numeric(smoking == 1),
    wc_provider_cor = as.numeric(wc_provider==1),
    second_opinion_cor = as.numeric(second_opinion == 4)) 

quiz_scores <- pn_quiz %>%
  select(id, training, total_score:second_opinion_cor) %>%
  group_by(training) %>%
  summarize(
    tot_score = round(mean(total_score/max_score)*100),
    wc_benefits = round(mean(wc_benefits_cor)*100),
    wc_medical_coverage = round(mean(wc_medical_coverage_cor)*100),
    on_job_injuries = round(mean(on_job_injuries_cor)*100),
    smoking = round(mean(smoking_cor)*100),
    wc_provider = round(mean(wc_provider_cor)*100),
    second_opinion = round(mean(second_opinion_cor)*100)) 

quiz_scores <- t(quiz_scores) %>%
  #paste0(., "%")
    as.data.frame() %>%
    rownames_to_column()

names(quiz_scores) <- c("Allias", "Pre", "Post1", "Post2")

quiz_scores <- quiz_scores %>%
  slice(-1) %>%
  mutate(
    Question = c("Mean total quiz score",
              "What kind of benefits does WC cover? (multiple choice)",
              "A caregiver will only get medical coverage through WC if their injury requires them to take time off of work",
              "Which are on-the-job injuries? (multiple choice)",
              "Stopping smoking can help caregivers recover after they are injured on the job",
              "The attending provider is the only provider covered under the WC claim",
              "Reasons for wanting to get a second opinion (multiple choice)"
              ),
    Pre = paste0(Pre, "%"),
    Post1 = paste0(Post1, "%"),
    Post2 = paste0(Post2, "%"),
    )

quiz_scores %>%
  select(Allias, Question, Pre:Post2) %>%
  kable(caption = paste0("Quiz scores before (Pre) and after (Post 1, Post 2) each training module. Percent of individuals who answered correctly. N = ", length(unique(pn_quiz$id)), ".")) %>%
  add_header_above(c(" " = 2, "Training" = 3))

```

```{r, eval=T}

quiz_scores.l <- quiz_scores %>%
  gather("Training", "Correct", Pre:Post2) %>%
  mutate(
    Training = factor(Training, levels = c("Pre", "Post1", "Post2")),
    Correct = as.numeric(substr(Correct, 1,  nchar(Correct)-1))/100,
    Allias = relevel(as.factor(Allias), ref = "tot_score")
         ) 

quiz_scores.l %>%
  ggplot(aes(x=Allias, y=Correct, fill=Training)) + 
  geom_bar(position = "dodge", stat = "identity") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  scale_y_continuous(labels = scales::percent) #+ 
  #labs(title = "Quiz scores before (Pre) and after (Post 1, Post 2) each training module.\nPercent of individuals who answered correctly.")

```

T-test comparing Pre-training vs Training 2 total quiz scores

```{r}

#reorganize total training scores
quiz_tot_scores <- pn_quiz %>%
  select(id, training, total_score) %>%
  spread(training, total_score, sep = "_")

(quiz_t_test <- t.test(x=quiz_tot_scores$training_0, 
       y= quiz_tot_scores$training_2))


quiz_t_p <- ifelse(round(quiz_t_test$p.value, 3) > 0.001, 
       round(quiz_t_test$p.value, 3), 
       "< 0.001")

#paste0("t-test p-val comparing pre-training to training 2 total quiz scores: ", quiz_t_p)

```

Wilcoxon Signed-Rank test. A non-parametric (paired) test of whether two distributions are identical without assuming them to be normally distributed. 

```{r}
(quiz_wilcox_test <- wilcox.test(x=quiz_tot_scores$training_0, 
       y= quiz_tot_scores$training_2, 
       paired = TRUE, 
       alternative = "two.sided")
)

quiz_wilcox_p <- ifelse(round(quiz_wilcox_test$p.value, 3) > 0.001, 
       round(quiz_wilcox_test$p.value, 3), 
       "< 0.001")


```

## Training & Program Feedback

```{r}

```




\newpage

# HCA Surveys

## Demographics

```{r}
############################### HCA Surveys ##################################################
##############################################################################################

######################################### Demographics #########################################
 
#Table 1  
hca %>%
    dplyr::summarize(
      N = n(),
      
      #age
      # [MISSING]
      # "Age (mean, SD)" = mean_sd()
      
      #gender
      "Female" = n_perc(Q2.55==1, na_rm = T),
      "Male" = n_perc(Q2.55==2, na_rm = T),
      "Gender Unknown" = n_perc(Q2.55==7, na_rm = T),
      
      #race
      ### --> why are surveys all single options? Nobody selected multiple races??
      "American Indian or Alaska Native" = n_perc(Q2.57 == 1, na_rm = T),
      "Asian" = n_perc(Q2.57 == 2, na_rm = T),
      "Black or African American" = n_perc(Q2.57 == 3, na_rm = T),
      "Native Hawaiian or Other Pacific Islander" = n_perc(Q2.57 == 4, na_rm = T),
      "White"= n_perc(Q2.57 == 5, na_rm = T),
      "Other Race" = n_perc(Q2.57 == 6, na_rm = T),
      "Race Unknown" = n_perc(Q2.57 == 7, na_rm = T),
      
      #hispanic
      "Yes" = n_perc(Q2.56 ==1, na_rm = T),
      "No" = n_perc(Q2.56 ==2, na_rm = T),
      "Origin Unknown" = n_perc(Q2.56 ==3, na_rm = T),
      
      #education
      # [MISSING]
      # "Less than high school" =  n_perc(___, na_rm = T),
      # "High school or GED" =   n_perc(___, na_rm = T),
      # "Some college" =   n_perc(___, na_rm = T),
      # "Finished college" =   n_perc(___, na_rm = T),
      # "Trade/vocational school" =   n_perc(___, na_rm = T),
      # "Other education" =   n_perc(___, na_rm = T),
      # "Education Unknown" =   n_perc(___, na_rm = T),
      
      #English 
      # [MISSING]
      # "English as a primary language" = n_perc(___, na_rm = T)
      ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  # drop rows w/ 0 entries
  filter(substr(V1, 1,1) != 0) %>%
  kable(caption = "Home Care Aide Demographics", 
        col.names = c("", "N (%)")
        ) %>%
  pack_rows("Gender", 2, 4,  bold = F, label_row_css = T) %>%
  pack_rows("Race", 5, 9,  bold = F, label_row_css = F) %>%
  pack_rows("Hispanic", 10, 12,  bold = F, label_row_css = F) %>%
  # #work around since bold=F doesn't work in pack_rows()
   gsub(pattern = "(<strong>)|<strong/>", replacement = "") %>%
  kable_styling()
  

```

## Employment

```{r}
######################################### Employment #########################################

hca %>%
    dplyr::summarize(
      N = n(),
      "Currently working as a HCA (n, %)" = n_perc(Q2.31==1, na_rm = T, show_denom = "never"),
      "Number of current clients (median)" = median(as.numeric(Q2.52_1_TEXT), na.rm = T),
      "Caregiver in own home (n, %)" = n_perc(Q2.53==1, na_rm = T)
      ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  # drop rows w/ 0 entries
  filter(substr(V1, 1,1) != 0) %>%
  kable(caption = "Home Care Aide Employment", 
        col.names = c("", "")
        ) %>%
  kable_styling()

```

## Reason for calling

note: The individual who responded "injury not at work" as the reason for her/his call answered the pain questions and is taking pain medication. She/he also filed an accepted worker's comp claim. Do we want to move this person to the "pain while working" category? 

### --> could look at call logs to verify reasons for calling? 

```{r}
hca %>%
  group_by("Reason for Calling" = Q2.2) %>%
  dplyr::summarize(
    N = n(),
    #N = paste0(n(), "/", nrow(.) ),
    Percent = paste0(round(N/nrow(.)*100), "%" ),
    Description = paste(Q2.3, collapse = "; "),
    #Description2 = writeLines(Q2.3)  #cat(paste(Q2.3), sep="\n") #cat(Q2.3, sep = "\n")
    #Description = linebreak(paste0(Q2.3, collapse ="\n" )   ) ,
    
  ) %>%
  kable(caption = paste0("Reason for calling the peer navigator line (n = ", nrow(hca), ")")) %>%
  kable_styling()

```

### --> ? 

```{r, results="asis"}
# ??? create a bulleted list

#cat(paste0("- `", names(iris), "`"), sep = "\n")

```



## Injury 

Note, only those who reported calling about injury responded to these questions, according to the survey logic.


```{r}
######################################### Injury #########################################

#tb <- 
  hca %>%
  filter(Q2.2_num %in% c(1:2)) %>%
  group_by(Q2.2) %>%
  dplyr::summarize(
    N = n(),
    #"Injury (n, %)" = paste0(n(), "/", nrow(hca), " (", round(n()/nrow(hca)*100), "%)" ),
   
   "Where did the injury occur?" = "",
    "Head" = n_perc(grepl("1", Q2.8[!is.na(Q2.8)]), show_denom = show_denom),  
   "Neck or throat" = n_perc(grepl("2", Q2.8[!is.na(Q2.8)]), show_denom = show_denom),
   "Back/trunk/torso" = n_perc(grepl("3", Q2.8[!is.na(Q2.8) ]), show_denom = show_denom),
   "Upper Extremities (shoulder, arm, hand)" = n_perc(grepl("4", Q2.8[!is.na(Q2.8) ]), show_denom = show_denom),
   "Lower extremities (hip, leg, foot)" = n_perc(grepl("5", Q2.8[!is.na(Q2.8) ]), show_denom = show_denom),
   "Other location" = n_perc(grepl("6", Q2.8[!is.na(Q2.8) ]), show_denom = show_denom),
   
   "How did the injury occur?" = "",
   "Overexertion or bodily reaction" = n_perc(Q2.7==1, show_denom = show_denom),
   "Slip, trip or fall" = n_perc(Q2.7==2, na_rm = T, show_denom = show_denom),
   "Exposure to harmful substance or environment" = n_perc(Q2.7==3, na_rm = T, show_denom = show_denom),
   "Transportation accident" = n_perc(Q2.7==4, na_rm = T, show_denom = show_denom),
   "Violent or physical contact by persons" = n_perc(Q2.7==5, na_rm = T, show_denom = show_denom),
   "Violent or physical contact by animals" = n_perc(Q2.7==6, na_rm = T, show_denom = show_denom),
   "Contact with moving or falling objects or equipment" = n_perc(Q2.7==7, na_rm = T, show_denom = show_denom),
   "Fire or explosion" = n_perc(Q2.7==8, na_rm = T, show_denom = show_denom),
   "Other" = n_perc(Q2.7==9, na_rm = T, show_denom = show_denom),
   )  %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  # rename columns that begin with "V" 
  row1_to_names() %>%
  kable(caption = "HCA Injury (N, %)") %>%
    add_indent(c(3:8, 10:18)) %>%
  kable_styling()

 
   

```



## Pain 

Note, only those who reported calling about injury responded to these questions, according to the survey logic.

```{r}
######################################### Pain #########################################

hca %>%
  filter(Q2.2_num %in% c(3:4)) %>%
  group_by(Q2.2) %>%
  dplyr::summarize(
   
   #Pain at work
    N = n(),
    #"Pain (n, %)" = paste0(n(), "/", nrow(hca), " (", round(n()/nrow(hca)*100), "%)" ),
   
   "Type of pain" = "",
   "Joint" = n_perc(grepl("1", Q2.19[!is.na(Q2.19)]), show_denom = show_denom),
   "Muscle" = n_perc(grepl("2", Q2.19[!is.na(Q2.19) ]), show_denom = show_denom),
   "Nerve" = n_perc(grepl("3", Q2.19[!is.na(Q2.19) ]), show_denom = show_denom),
   "Other" = n_perc(grepl("4", Q2.19[!is.na(Q2.19) ]), show_denom = show_denom),
   
   "Pain duration" = "",
   "Days" = n_perc(Q2.22==1, na_rm = T, show_denom = show_denom),
   "Weeks" = n_perc(Q2.22==2, na_rm = T, show_denom = show_denom),
   "Months" = n_perc(Q2.22==3, na_rm = T, show_denom = show_denom),
   "Years" = n_perc(Q2.22==4, na_rm = T, show_denom = show_denom),
   
   "Pain Location" = "",
   "Head" = n_perc(grepl("1", Q2.21[!is.na(Q2.21)]), show_denom = show_denom),
   "Neck or throat" = n_perc(grepl("2", Q2.21[!is.na(Q2.21)]), show_denom = show_denom),
   "Back/trunk/torso" = n_perc(grepl("3", Q2.21[!is.na(Q2.21)]), show_denom = show_denom),
   "Upper Extremities (shoulder, arm, hand)" = n_perc(grepl("4", Q2.21[!is.na(Q2.21)]), show_denom = show_denom),
   "Lower extremities (hip, leg, foot)" = n_perc(grepl("5", Q2.21[!is.na(Q2.21) ]), show_denom = show_denom),
   "Other" = n_perc(grepl("6", Q2.21[!is.na(Q2.21)]), show_denom = show_denom),

   "Known medical condition as etiology of pain" = n_perc(Q2.20==1, na_rm = T, show_denom = show_denom)
  ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  # # drop rows w/ 0 entries
  #                                 # no V2 column
  # filter(!(substr(V1, 1,1) == 0 #& substr(V2, 1,1) == 0
  #          )) %>%
   # rename columns that begin with "V" 
  row1_to_names() %>%
  kable(caption = "HCA Pain") %>%
    add_indent(c(3:6, 8:11, 13:17)) %>%
  kable_styling()
    
```


## Interventions for Injury and Chronic Musculoskeletal Pain

Work-related injury or pain (n = `r sum(grepl("1|3", hca$Q2.2_num))`): Modified duty

If denominators seem off, it's likely due to individuals choosing not to respond to some questions.

```{r}
######################################### Interventions #########################################

hca %>%
    filter(Q2.2_num %in% c(1,3)) %>%
  mutate(
    Q2.2 = recode_factor(factor(Q2.2),
                         "1" = "Injury at work",
                         "3" = "Pain while working",
                         )
    ) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
   
   "Performing modified duty" = n_perc(Q2.33 == 1, na_rm = T, show_denom = "always"),
   "Q2.33 - prefer not to answer" = n_perc(Q2.33 == 3, na_rm = T, show_denom = "always"),
   
   "If performing modified duty, nature of modified duty" = "",
   "Not working at all" = n_perc(Q2.34 == 6, na_rm = T, show_denom = "always"),
   "Working few hours" = n_perc(Q2.34 == 1, na_rm = T, show_denom = "always"),
   "Not doing certain tasks" = n_perc(Q2.34 == 2, na_rm = T, show_denom = "always"),
   "Using tools or equipment to do certain tasks" = n_perc(Q2.34 == 3, na_rm = T, show_denom = "always"),
   "Other modification" = n_perc(Q2.34 == 4, na_rm = T, show_denom = "always"),
   
   "Provider category for recommended modified duty" = "",
   "The attending provider for my workers’ compensation claim prescribed the restrictions" = n_perc(Q2.35 == 1, na_rm = T, show_denom = "always"),
   "Another health care provider recommended the restrictions" = n_perc(Q2.35 == 2, na_rm = T, show_denom = "always"),
    "My client’s case manager recommended the restrictions" = n_perc(Q2.35 == 3, na_rm = T, show_denom = "always"),
     "I restricted my work/made accommodations on my own" = n_perc(Q2.35 == 4, na_rm = T, show_denom = "always"),
   "Other modification approach strategy" = n_perc(Q2.35 == 5, na_rm = T, show_denom = "always"),
   "Prefer not to answer"= n_perc(Q2.35 == 6, na_rm = T, show_denom = "always")
   ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
   # rename columns that begin with "V" 
  row1_to_names() %>%
  kable(caption = "Work-related injury or pain: Modified duty",  
        #row.names = T
        ) %>% 
  add_indent(c(2, 4:8, 10:15)) %>%
  kable_styling()

```

Injury or pain (n = `r sum(grepl("1|2|3|4", hca$Q2.2_num))`): Medical care, medication & other resources used

```{r}
hca %>%
    filter(Q2.2_num %in% c(1:4)) %>%
  mutate(
    Q2.40_1_TEXT = recode_factor(factor(Q2.40_1_TEXT),
                                 "PT, physical therapy and massage therapy" = "PT, massage",
                                 "Tryed physical therapy" = "PT",
                                 "Massage and fusions and cyphoplasties" = "Massage, Kyphoplasty"
                                 )
    ) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    N = n(),
   "Type of medical care sought (select all that apply)" = "",
            #multiple options selected
   "None" = n_perc(grepl("1", Q2.36[!is.na(Q2.36)]), show_denom = show_denom),  
   "First aid" = n_perc(grepl("2", Q2.36[!is.na(Q2.36)]), show_denom = show_denom),
   "Treatment in a clinic by an occupational health provider" = n_perc(grepl("3", Q2.36[!is.na(Q2.36)]), show_denom = show_denom),  
   "Rehabilitative therapies (such as massage, physical therapy, occupational therapy, chiropractic care, acupuncture, etc.)."= n_perc(grepl("4", Q2.36[!is.na(Q2.36)]), show_denom = show_denom),
   "Treatment at an emergency room" = n_perc(grepl("5", Q2.36[!is.na(Q2.36)]), show_denom = show_denom),
   "Other care" = n_perc(grepl("6", Q2.36[!is.na(Q2.36)]), show_denom = show_denom),
   "Other care - details" = paste0(unique(Q2.36_6_TEXT[!is.na(Q2.36_6_TEXT)]), collapse = "; "),
   
   "Taking pain medication" = n_perc(Q2.37 == 1, na_rm = T, show_denom = show_denom),
   "If taking pain medicdation, what kind (select all that apply)" = "",
  
        # multiple options
   "Non-prescription medications (Over-the-counter medications)" = n_perc(grepl("1", Q2.38[!is.na(Q2.38)]), show_denom = show_denom),  
        "Prescription medications" = n_perc(grepl("2", Q2.38[!is.na(Q2.38)]), show_denom = show_denom),  
   "Other medication" = n_perc(grepl("3", Q2.38[!is.na(Q2.38)]), show_denom = show_denom),  
   
   "Used other resources to help with injury or pain" = n_perc(Q2.40 == 1, na_rm = T, show_denom = show_denom),
   
   "Other resources used" = paste0(unique(Q2.40_1_TEXT[!is.na(Q2.40_1_TEXT)]), collapse = "; "),
   
   # this Q is similar to the Q later (Q2.29) about availability specifically after injury/pain? 
   "General availability of respite care" = "",
   "Never/rarely" = n_perc(Q2.54 == 1, na_rm = T, show_denom = show_denom),
   "Sometimes" = n_perc(Q2.54 == 2, na_rm = T, show_denom = show_denom),
   "Usually/always" = n_perc(Q2.54 == 3, na_rm = T, show_denom = show_denom),
   "Q2.54 - Prefer not to answer" = n_perc(Q2.54 == 4, na_rm = T, show_denom = show_denom),
   
   ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
   # rename columns that begin with "V" 
  row1_to_names() %>%
  kable(caption = "Injury or pain: Medical care, medication & other resources used", 
        #row.names = T
        )  %>%
  add_indent(c(3:9, 11:14, 16, 18:21)) %>%
  kable_styling()
   
```

Injury (n = `r sum(grepl("1|2", hca$Q2.2_num))`): Worker's Compensation

```{r}
hca %>%
  # only these respondants answered these questions
  filter(Q2.2_num %in% c(1:2)) %>%
  mutate(Q2.2 = recode_factor(factor(Q2.2),
                              "1" = "Injury at work",
                              "2" = "Injury not at work"
                              )) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    "Had filed or working on a claim" = n_perc(Q2.9 %in% c(1, 2), na_rm = T, show_denom = "always"),
    "Had filed a claim prior to the initial peer navigator call" = n_perc(Q2.9==1, na_rm = T, show_denom = "always"),
    "Still working on paperwork but have not filed yet" = n_perc(Q2.9==2, na_rm = T, show_denom = "always"),
    
    # Q2.9 - Prefer not to answer 
    
        "Received help filing paperwork" = n_perc(Q2.11==1, na_rm = T, show_denom = "always"),
    #"Received help filing paperwork from a peer navigator" = n_perc(Q2.12==1, na_rm = T, show_denom = "always"),
    "Needed to find a new health care provider to open or manage claim" = n_perc(Q2.15==1, na_rm = T, show_denom = "always"),
 "Mostly or completely satisfied with the process of finding a new provider" = n_perc(Q2.16[!is.na(Q2.16)] %in% c(3,4), na_rm = T, show_denom = "always"),
 
 # this question was accidentally asked to everyone. only show the responses of those who said they had filed or were working on filing a claim: Q2.9 %in% c(1, 2)
 "Is comfortable interacting with his/her claim manager at Labor and Industries about his/her workers’ compensation claim (agree or stronly agree)" = n_perc(Q2.50_6[Q2.9 %in% c(1, 2)] %in% c(4:5), na_rm = T, show_denom = "always", digits = 0), 
 
 
 "Claim status" = "", 
 "Still filing paperwork" = n_perc(Q2.13==1, na_rm = T, show_denom = "always"),
 "Awaiting initial decision" = n_perc(Q2.13==2, na_rm = T, show_denom = "always"),
 "Accepted, claim is currently open" = n_perc(Q2.13==3, na_rm = T, show_denom = "always"),
 "Accepted, claim is currently closed" = n_perc(Q2.13==4, na_rm = T, show_denom = "always"),
 "Denied, appealing decision" = n_perc(Q2.13==5, na_rm = T, show_denom = "always"),
 "Denied, not appealing decision" = n_perc(Q2.13==6, na_rm = T, show_denom = "always"),
 
 "Mostly or completely satisfied with the claim filing process" = n_perc(Q2.14[!is.na(Q2.13)] %in% c(3,4), na_rm = T, show_denom = "always"),
 
 "Reason if a claim was not filed"= "",
 "Not eligible" = n_perc(Q2.10 == 1, na_rm = T, show_denom = "always"),
 "Didn't feel it was necessary" = n_perc(Q2.10 == 2, na_rm = T, show_denom = "always"),
 "Didn't have time" = n_perc(Q2.10 == 3, na_rm = T, show_denom = "always"),
 "Didn't know how" = n_perc(Q2.10 == 4, na_rm = T, show_denom = "always"),
 "Didn't want to go to the doctor/clinic" = n_perc(Q2.10 == 5, na_rm = T, show_denom = "always"),
 "Didn't want to file paperwork with L&I" = n_perc(Q2.10 == 6, na_rm = T, show_denom = "always"),
 "Other reason" = n_perc(Q2.10 == 7, na_rm = T, show_denom = "always"),
  ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
   # rename columns that begin with "V" 
  row1_to_names() %>%
  kable(caption = "Injury: Worker's Compensation", 
        #row.names = T
        ) %>% 
  add_indent(c(2:3, 6, 9:14, 17:23)) %>%
  kable_styling()

```


Injury or pain (n = `r sum(grepl("1|2|3|4", hca$Q2.2_num))`): Impact

```{r}
hca %>%
    filter(Q2.2_num %in% c(1:4)) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
   "Working with pain or injury" = n_perc(Q2.25 == 1, na_rm = T, show_denom = "always"),
   "Missed work because of pain or injury" = n_perc(Q2.26 == 1, na_rm = T, show_denom = "always"),
   "Days missed (n; mean, SD)" = mean_sd(as.numeric(Q2.27_1_TEXT), na_rm = T, denote_sd = "paren", show_n = "always", 
                                      ),
   
   "Received time loss" = "",
    "Yes, wage replacement/time loss from my workers’ compensation claim/Labor & Industries" = n_perc(Q2.28==1, na_rm = T, show_denom = "always"),
   "Yes, paid time off or sick leave through Washington State Department of Social and Health Services" = n_perc(Q2.28==2, na_rm = T, show_denom = "always"),
   "Yes, other" = n_perc(Q2.28==3, na_rm = T, show_denom = "always"),
   "No" = n_perc(Q2.28==4, na_rm = T, show_denom = "always"),
   
   "Respite coverage available during injury or pain" = "",
   "All the days off I needed were covered" = n_perc(Q2.29 == 1, na_rm = T, show_denom = "always"),
   "Some of the days off I needed were covered" = n_perc(Q2.29 == 2, na_rm = T, show_denom = "always"),
   "None of the days off I needed were covered" = n_perc(Q2.29 == 3, na_rm = T, show_denom = "always"),
   "Not applicable - I did not need coverage" = n_perc(Q2.29 == 4, na_rm = T, show_denom = "always"),
   "Q2.29 - Prefer not to answer" = n_perc(Q2.29 == 5, na_rm = T, show_denom = "always"),
   
   "Lost clients due to time off after injury or pain" = n_perc(Q2.30 == 1, na_rm = T, show_denom = "always"),
   
  ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "Injury or pain: Impact", 
        #row.names = T
        )  %>%
  add_indent(c(3, 5:8, 10:14)) %>%
  kable_styling()

```

 

## Pre-Post: Work, Pain and Injury

```{r}

hca %>%
    filter(Q2.2_num %in% c(1:4)) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    N = n(),
   "Excellent" = n_perc(Q2.41 == 1, na_rm = T, show_denom = show_denom),
   "Very good" = n_perc(Q2.41 == 2, na_rm = T, show_denom = show_denom),
   "Good" = n_perc(Q2.41 == 3, na_rm = T, show_denom = show_denom),
   "Fair" = n_perc(Q2.41 == 4, na_rm = T, show_denom = show_denom),
   "Poor" = n_perc(Q2.41 == 5, na_rm = T, show_denom = show_denom),
   "Q2.41 - Prefer not to answer" = n_perc(Q2.41 == 1, na_rm = T, show_denom = show_denom),
   
  ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "General health status")  %>%
  kable_styling()


```

```{r}
hca %>%
    filter(Q2.2_num %in% c(1:4)) %>%
  mutate(
    #subtract 1 b/c of coding
    Q2.48 = as.numeric(Q2.42)-1,
    ) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    N = n(), 
      "Pain level over the last 7 days, 0-10 (mean, SD)" = mean_sd(Q2.48, na_rm = T, denote_sd = "paren", show_n = show_denom),  
 
  ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "Pain level", 
        #row.names = T
        )  %>%
  #add_indent(c(3, 5:8, 10:14)) %>%
  kable_styling()
```


```{r, about scoring}
#http://www.reillyassociates.net/WPAI_Scoring.html  
#WPAI outcomes are expressed as impairment percentages, with higher numbers indicating greater impairment and less productivity, i.e., worse outcomes, as follows: 

# Questions:
# 1 = currently employed
# 2 = hours missed due to health problems
# 3 = hours missed other reasons
# 4 = hours actually worked
# 5 = degree health affected productivity while working
# 6 = degree health affected regular activities
# 
# Scores:
# Multiply scores by 100 to express in percentages.
# 
# Percent overall work impairment due to health:
#       Q2/(Q2+Q4)+[(1-(Q2/(Q2+Q4)))x(Q5/10)]
# 
# Percent activity impairment due to health: 
#   Q6/10 
#   Q2.47/10

```


```{r}
hca %>%
    filter(Q2.2_num %in% c(1:4)) %>%
  mutate(
    #subtract 1 b/c of coding
    Q2.42 = as.numeric(Q2.42)-1,
    Q2.47 = as.numeric(Q2.47)-1,
    Q2.48 = as.numeric(Q2.42)-1,
    ) %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    N = n(), 
   "Current work ability, 0-10 (mean, SD)" = mean_sd(Q2.42, na_rm = T, denote_sd = "paren", show_n = show_denom),
   
                                                              #Q6/10 
   "Percent activity impairment due to health (mean, SD)" = mean_sd(Q2.47/10*100, na_rm = T, denote_sd = "paren", show_n = show_denom), 
   "Pain level over the last 7 days, 0-10 (mean, SD)" = mean_sd(Q2.48, na_rm = T, denote_sd = "paren", show_n = show_denom),  
 
  ) %>%
  t() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "Impact of health problems on work", 
        #row.names = T
        )  %>%
  #add_indent(c(3, 5:8, 10:14)) %>%
  kable_styling()

```


```{r}
#hca[c("Q2.2", "Q2.43_1_TEXT", "Q2.45_1_TEXT", "Q2.46")] %>% View()

hca %>%
  filter(Q2.2_num %in% c(1:4)) %>%
  mutate(   
  #subtract 1 b/c of coding
    Q2.46 = Q2.46-1, #) %>%
  #select(Q2.2, Q2.2_num, Q2.43_1_TEXT, Q2.45_1_TEXT, Q2.46) %>%
  # Q2/(Q2+Q4)+[(1-(Q2/(Q2+Q4)))x(Q5/10)]
  #mutate(
    value = Q2.43_1_TEXT/(Q2.43_1_TEXT + Q2.45_1_TEXT) + ((1-(Q2.43_1_TEXT/(Q2.43_1_TEXT + Q2.45_1_TEXT)))*(Q2.46/10)),
         value = value*100
  ) %>%
  drop_na(value) %>%
  group_by(Q2.2) %>%
  dplyr::summarize(
    N = n(),
    "Percent of overall work impairment due to health (mean, SD)" = mean_sd(value, na_rm = T, denote_sd = "paren", digits = 0)
  ) %>%
  t() %>% 
  as.data.frame() %>% rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "Impact of health problems on work",
        )  %>%
  kable_styling()


```

Job demands (Agree or strongly agree)

```{r}
# hca%>%
#   select(Q2.2, contains("Q2.49")) %>%
#   summary()

hca %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    N = n(),
    "On my job, I have very little freedom to decide how I do my work." = n_perc(Q2.49_1 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "My job allows me to make a lot of decisions on my own." = n_perc(Q2.49_2 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "My job security is good." = n_perc(Q2.49_3 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "My job is emotionally demanding." = n_perc(Q2.49_4 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "I have enough time to get the job done." = n_perc(Q2.49_5 %in% c(4:5), na_rm = T, show_denom = show_denom ),
     "My job requires working very hard." = n_perc(Q2.49_6 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "My job requires me to do repeated lifting, pushing, pulling, or bending." = n_perc(Q2.49_7 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "My job regularly requires me to perform repetitive or forceful hand movements." = n_perc(Q2.49_8 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    ) %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "Job demands (agree or strongly agree)")  %>%
  kable_styling()


```

Comfort level and access to resources

```{r}
 
hca %>%
  group_by(Q2.2) %>% 
  dplyr::summarize(
    N = n(),
     "When I have questions about my health and safety related to work, I know who to ask or where to find the answer." = n_perc(Q2.50_1 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "I feel comfortable asking for help when I have questions about my health and safety at work." = n_perc(Q2.50_2 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "I am comfortable refusing unsafe work." = n_perc(Q2.50_3 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "I am comfortable with the idea of filing a workers’ compensation claim (for current or  possible future work-related injury)." = n_perc(Q2.50_4 %in% c(4:5), na_rm = T, show_denom = show_denom ),
    "I am comfortable interacting with clients’ case managers about my needs for my own health and safety at work." = n_perc(Q2.50_5 %in% c(4:5), na_rm = T, show_denom = show_denom ), 
    # move this question to the worker's compensation section since this was only supposed to have been asked to people who had filed or were working on filing a claim
    #"I am comfortable interacting with my claim manager at Labor and Industries about my workers’ compensation claim." = n_perc(Q2.50_6 %in% c(4:5), na_rm = T, show_denom = show_denom ), 
    "I am comfortable interacting with health care providers about my injury and/or pain." = n_perc(Q2.50_7 %in% c(4:5), na_rm = T, show_denom = show_denom ), 
    "I am confident I would be able to get the help I need if I had a work-related injury in the future." = n_perc(Q2.50_8 %in% c(4:5), na_rm = T, show_denom = show_denom ), 
    "I would be comfortable filing a workers’ compensation claim If I had a work-related injury in the future." = n_perc(Q2.50_9 %in% c(4:5), na_rm = T, show_denom = show_denom ), 
    
  ) %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var = "Measure") %>%
  row1_to_names() %>%
  kable(caption = "Comfort level and access to resources (agree or strongly agree)")  %>%
  kable_styling()

```

  
  
  
  
## Program Feedback

```{r}
###################################### Program Feedback #####################################

```



# Call Logs 

```{r}
######################################### Call Logs #########################################

```















\newpage
# Code

```{r,ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60), include=T}
```

 